---
title: "Preliminary analysis Sample PV73, LV73"
author:
  - "trnguyen@ukaachen.de"
date: "Last update on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: no
    df_print: paged
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 3
    number_sections: true
    theme: lumen
params:
  batch.id: NA
---


```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

<style type="text/css">
    div.datatables { height: auto !important;}
</style>

**Note on the .html report: Click on the image to zoom-in and one more click to go back to the original**

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.height=10, fig.width=18}
##### clean up #####
# gc()
# rm(list = ls())

path.to.project.src <- "/home/hieunguyen/CRC1382/src_2023/ABeckers"

source(file.path(path.to.project.src, "00_import_libraries.R"))
source(file.path(path.to.project.src, "00_helper_functions.R"))

path.to.src <- "/home/hieunguyen/CRC1382/src_2023/src_pipeline/scRNA_GEX_pipeline/processes_src"
source(file.path(path.to.src, "s8_integration_and_clustering.R"))

#####----------------------------------------------------------------------#####
# CONFIGURATIONS AND PREPRATIONS
#####----------------------------------------------------------------------#####
PROJECT <- "ABeckers_data"
path.to.storage <- "/media/hieunguyen/HD01/storage"
outdir <- "/home/hieunguyen/CRC1382/outdir"
# batch.id <- "batch1"
batch.id <- params$batch.id

path.to.main.input <- file.path(outdir, PROJECT, batch.id)
s.obj <- readRDS(file.path(path.to.main.input, "s8_output", sprintf("%s.output.s8.rds", PROJECT)))
s.obj <- subset(s.obj, Doublet_classifications == "Singlet")

path.to.main.output <- file.path(path.to.main.input, "data_analysis")
dir.create(path.to.main.output, showWarnings = FALSE, recursive = TRUE)

path.to.01.output <- file.path(path.to.main.output, "01_output")
dir.create(path.to.01.output, showWarnings = FALSE, recursive = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.height=10, fig.width=18}
if (file.exists(file.path(path.to.01.output, "DE_cluster_marker_genes.rds")) == FALSE){
  cluster.markers <- FindAllMarkers(object = s.obj, assay = "RNA", test.use = "wilcox")
  cluster.markers <- subset(cluster.markers, cluster.markers$p_val_adj < 0.05 & cluster.markers$avg_log2FC > 0)
  saveRDS(cluster.markers, file.path(path.to.01.output, "DE_cluster_marker_genes.rds"))
} else {
  cluster.markers <- readRDS(file.path(path.to.01.output, "DE_cluster_marker_genes.rds"))
}

```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.height=10, fig.width=18}
##### Add TSNE
s.obj <- RunTSNE(s.obj, reduction = "INTE_PCA", dims = 1:30, reduction.name="INTE_TSNE")
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.height=10, fig.width=18}
# convert.stage <- list(Sample_3 = "PV", Sample_4 = "LV")
# 
# meta.data <- s.obj@meta.data %>% rownames_to_column("barcode") %>%
#   rowwise() %>%
#   mutate(stage = convert.stage[[stage]]) %>%
#   column_to_rownames("barcode")
# 
# s.obj <- AddMetaData(object = s.obj, metadata = meta.data$stage, col.name = "stage")
```

# Preprocessing and QC for GEX data
## Raw data Quality control  {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$all.QC)){
 
    cat('###',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$all.QC[plot.name])
    cat(' \n \n')
}
```



## Ambient RNA background correction 

### DecontX clusters {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$ambient.cluster.RNA.plot)){
 
    cat('####',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$ambient.cluster.RNA.plot[plot.name])
    cat(' \n \n')
}
```

### Contamination level in each sample

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
ggplot(s.obj@meta.data, aes(x=name, y=AmbientRNA)) + 
  geom_boxplot()

```


### Ambient RNA contamination level {.tabset}

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$ambient.contamination.plot)){
 
    cat('####',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$ambient.contamination.plot[plot.name])
    cat(' \n \n')
}
```


## Descriptive statistics and filtering threshold {.tabset}
This section is devoted to the descriptive statistics of the following varialbes: `nFeature_RNA, nCount_RNA, percent.mt, percent.ribo`. 

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.item in c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.ribo")){
  boxplot <- s.obj@meta.data %>% ggplot(aes_string(x = "name", y = plot.item)) +
    geom_boxplot(outlier.colour="black", outlier.shape=16,
               outlier.size=2, notch=FALSE) +
    ggtitle(sprintf("Boxplot: Distribution of %s in each dataset", plot.item))
  cat('###', plot.item,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
  
  print(boxplot)
  
  cat(' \n \n')
}
```



## Descriptive statistics + TSNE {.tabset}

### % Mitochondrial
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "INTE_TSNE", feature = "percent.mt", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % Ribosome
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "INTE_TSNE", feature = "percent.ribo", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % nCount RNA
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "INTE_TSNE", feature = "nCount_RNA", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % nGenes 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "INTE_TSNE", feature = "nFeature_RNA", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

## Cell cycle scoring {.tabset}

### Cell cycle, split by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(s.obj, reduction = "INTE_TSNE", split.by = "Phase")
```

### Cell cycle, group by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(s.obj, reduction = "INTE_TSNE", group.by = "Phase", label = TRUE, label.size = 8, pt.size = 0.5, label.box = TRUE, repel = TRUE)
```

### PCA, cell cycle, group by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
all.genes <- rownames(x = s.obj)
s.genes <- paste0("^", cc.genes$s.genes, "$", collapse = "|")
s.genes <- all.genes[grepl(s.genes, all.genes, ignore.case = TRUE)]
g2m.genes <- paste0("^", cc.genes$g2m.genes, "$", collapse = "|")
g2m.genes <- all.genes[grepl(g2m.genes, all.genes, ignore.case = TRUE)]
s.obj <- RunPCA(s.obj, features = c(s.genes, g2m.genes), nfeatures.print = 10, reduction.name="CELLCYCLED_PCA")

DimPlot(s.obj, reduction = "CELLCYCLED_PCA", group.by = "Phase", pt.size = 1)
```

# Dimension reduction with TSNE

## TSNE: all clusters 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object = s.obj, reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE) + 
  ggtitle(sprintf("TSNE: All clusters")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```

## TSNE: all samples
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object = s.obj, reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE, group.by = "name") + 
  ggtitle(sprintf("TSNE Sample: All samples after integrating")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```

## TSNE: LV samples
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object = subset(s.obj, stage == "LV"), reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE, group.by = "name") + 
  ggtitle(sprintf("TSNE Sample: All samples after integrating")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```

## TSNE: LV samples only, labeled by clusters
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object = subset(s.obj, stage == "LV"), reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE, group.by = "seurat_clusters") + 
  ggtitle(sprintf("TSNE Sample: All samples after integrating")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```


## TSNE: PV samples
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object =  subset(s.obj, stage == "PV"), reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE, group.by = "name") + 
  ggtitle(sprintf("TSNE Sample: All samples after integrating")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```


## TSNE: PV samples only, labeled by clusters
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(object = subset(s.obj, stage == "PV"), reduction = "INTE_TSNE", label = TRUE, label.box = TRUE, label.size = 10, pt.size = 1, repel = TRUE, group.by = "seurat_clusters") + 
  ggtitle(sprintf("TSNE Sample: All samples after integrating")) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"))
```


# Hashtag-Antibodies data (ADT)
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DefaultAssay(s.obj) <- "ADT"

counts.adt <- GetAssayData(s.obj, slot = "counts", assay = "ADT")
s.obj.HTO <- CreateSeuratObject(counts = counts.adt, assay = "HTO")

s.obj.HTO <- NormalizeData(s.obj.HTO, normalization.method = "CLR")

```

## Histogram: Raw count number of hashtags per cell {.tabset}
Histogram: Raw count number of hashtags per cell: 

- x-axis: Number of hashtags per cell

- y-axis: Number of cells

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (ht in unique(row.names(s.obj.HTO))){
  hashtag.counts <- counts.adt[ht, ] %>% as.data.frame()
  colnames(hashtag.counts) <- c("count")
  cat(sprintf("### Hashtag: %s \n", ht))
  p <- ggplot(subset(hashtag.counts, hashtag.counts$count >= 0), aes(x = count)) + geom_histogram(bins = max(hashtag.counts$count)) + ggtitle(ht) + 
    theme(text = element_text(size=20), 
          axis.text.x = element_text(hjust=1, size = 20),
          axis.text.y = element_text(hjust=1, size = 20)) 
  print(p)
  cat("\n \n")
}
```

## Histogram: log-transformed raw counts of hashtags per cell {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (ht in  unique(row.names(s.obj.HTO))){
  counts.adt.ht123 <- GetAssayData(s.obj.HTO, slot = "counts")
  hashtag.counts <- log2(counts.adt.ht123)[ht, ] %>% as.data.frame()
  colnames(hashtag.counts) <- c("count")
  cat(sprintf("### Hashtag: %s \n", ht))
  p <- ggplot(subset(hashtag.counts, hashtag.counts$count >= 0), aes(x = count)) + geom_histogram(bins = 10) + 
    ggtitle(ht)  + 
    theme(text = element_text(size=20), 
          axis.text.x = element_text(hjust=1, size = 20),
          axis.text.y = element_text(hjust=1, size = 20)) 
  print(p)
  cat("\n \n")
}
```

## Assigned cut-off 
```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
# s.obj.HTO <- HTODemux(s.obj.HTO, assay = "HTO", positive.quantile = 0.99)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
# Idents(s.obj.HTO) <- factor(x = Idents(s.obj), levels = levels(s.obj))
```

## Illustration by Ridge plots, Hashtag-Antibodies expression values in each cluster {.tabset}

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=12, fig.height=12}
for (hashtag in rownames(s.obj.HTO[["HTO"]])){
  cat(sprintf("### %s \n", hashtag))
  p <- RidgePlot(s.obj.HTO, assay = "HTO", features = hashtag) +
    theme(legend.position = "none")
  print(p)
  cat("\n \n")
}
```


## Illustration by Violin plot {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=12, fig.height=12}

for (hashtag in rownames(s.obj.HTO[["HTO"]])){
  cat(sprintf("### %s \n", hashtag))
  p <- VlnPlot(s.obj.HTO, assay = "HTO", features = c(hashtag)) + theme(legend.position = "none")
  print(p)
  cat("\n \n")
}
```

# Cluster marker genes

Identify differentially expressed genes in each cluster. 

## Feature plot {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (cluster.id in sort(unique(s.obj@meta.data$seurat_clusters))){
  DefaultAssay(s.obj) <- "RNA"
  cat(sprintf("### Cluster %s \n", cluster.id))
  tmp.cluster.markers <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
  p <- FeaturePlot(object = s.obj, reduction = "INTE_TSNE", features = head(tmp.cluster.markers, 12)$gene, ncol = 3, label = TRUE, pt.size = 0.5, label.size = 5, label.color = "red")  
  print(p)
  cat("\n \n")
}
```

## Dot plot{.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (cluster.id in sort(unique(s.obj@meta.data$seurat_clusters))){
  DefaultAssay(s.obj) <- "RNA"
  cat(sprintf("### Cluster %s \n", cluster.id))
  tmp.cluster.markers <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
  p <- DotPlot(object = s.obj, features = head(tmp.cluster.markers, 12)$gene)  
  print(p)
  cat("\n \n")
}
```

## Violin plot{.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (cluster.id in sort(unique(s.obj@meta.data$seurat_clusters))){
  DefaultAssay(s.obj) <- "RNA"
  cat(sprintf("### Cluster %s \n", cluster.id))
  tmp.cluster.markers <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
  p <- VlnPlot(object = s.obj, features = head(tmp.cluster.markers, 12)$gene)  
  print(p)
  cat("\n \n")
}
```

## Full tables of DE genes {.tabset}
```{r echo=FALSE, results='asis', include=FALSE}
cluster.markers %>% create_dt()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
all.cluster.ids <- sort(unique(s.obj$seurat_clusters))
for (cluster.id in all.cluster.ids){
  tmp.table <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
cat(paste("\n\n### Cluster: ", cluster.id, "##\n"))
  print( htmltools::tagList(datatable(tmp.table, extensions = 'Buttons',
                filter = "top",
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All")),
                               columnDefs = list(list(
                                 targets = "_all",
                                 render = JS(
                                   "function(data, type, row, meta) {",
                                   "return type === 'display' && data != null && data.length > 100 ?",
                                   "'<span title=\"' + data + '\">' + data.substr(0, 100) + '...</span>' : data;",
                                   "}")
                               ))
                ))))
  cat("\n \n")  
}
```

# Some marker genes for cell types


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
# convert.name.to.sampleid <- list(Sample_3 = "PV73",
#                                  Sample_4 = "LV73")
# meta.data <- s.obj@meta.data %>% rownames_to_column("barcode") %>%
#   rowwise() %>%
#   mutate(name = convert.name.to.sampleid[[name]]) %>%
#   mutate(stage = ifelse(name == "LV73", "LV", "PV")) %>% 
#   as.data.frame() %>%
#   column_to_rownames("barcode")
# 
# meta.data <- meta.data[row.names(s.obj@meta.data), ]
# s.obj <- AddMetaData(object = s.obj, metadata = meta.data$name, col.name = "name")
# s.obj <- AddMetaData(object = s.obj, metadata = meta.data$stage, col.name = "stage")

if (file.exists(file.path(path.to.01.output, sprintf("%s.rds", batch.id))) == FALSE){
  saveRDS(s.obj, file.path(path.to.01.output, sprintf("%s.rds", batch.id)))  
}
```
